### 2018-11-28 museum.tex
more SN proof

% A museum of no-longer-needed lemmas and such (fragments of proofs of which may however become useful later)

>>>>

% A museum of no-longer-needed lemmas and such (fragments of proofs of
% which may however become useful later)

\begin{lemma}\label{lem_reducible_type}
  If $\tau$ is a type and $t \in \val{\tau}{\xi}{\omega}$ then
  $t : \omega(\tau)$.
\end{lemma}

\begin{proof}
  Let~$\varphi$ be a type constructor. By induction on the kind
  of~$\varphi$ we define when $\val{\varphi}{\omega}{\xi}$ is
  \emph{good}:
  \begin{itemize}
  \item if $\varphi$ is a type then $\val{\varphi}{\xi}{\omega}$ is
    good when $t \in \val{\varphi}{\xi}{\omega}$ implies
    $t : \omega(\varphi)$,
  \item if $\varphi$ has kind~$\kappa_1\arrkind\kappa_2$ then
    $\val{\varphi}{\xi}{\omega}$ is good when
    $\val{\varphi}{\xi[\subst{\alpha}{X}]}{\omega[\subst{\alpha}{\tau}]}$
    is good for every $\tau \in \Tc_{\kappa_1}$ and every
    $X \in \Cb_\tau$.
  \end{itemize}
  Now prove by induction on~$\varphi$
  that~$\val{\varphi}{\omega,\xi}{}$ is good.

  TODO
\end{proof}

Thus, we have:

\begin{lemma}\label{lem_abusive_notation}
  Every interpretation term has the form $s t_1 \dots t_n$ with $s$ a
  variable, function symbol or abstraction $\abstraction{a}{s'}$ (for
  $n \geq 0$), or $s$ a natural number and $n = 0$.
\end{lemma}

\begin{proof}
By induction on the size of interpretation terms (and a simple case
analysis).\qed
\end{proof}
